---
title: "ANLY 502 Group Project Report"
author:
 - "Akpany Benjamin Ebby"
 - "Amit Augustine"
 - "Zongxia Li"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    highlight: zenburn
comment: Rmd Document with Markdown + Embedded R Code
---

#### Document as of `r Sys.Date()`

## Introduction

The world is moving fast towards a digital future, which encompasses people being Always On, Always Connected, and sharing a global network of information, as Data. Hence, we have the cloud revolution rapidly expanding in all spheres of our digital world, where all our information -self-created or even 3rd party sourced - is hosted and stored online in cyberspace. 
But, an often-overlooked factor in this cloud revolution and even transitional information processing and storage, was cybersecurity. 
Nowadays, there is tremendous focus on cybersecurity, due to risk of various security threats, amplified due to all the information stored online. We have various cybersecurity threat mitigation tools like vulnerability scanners, hybrid firewalls and Intrusion prevention systems, smart endpoint tools, honeypot techniques etc.
'Honeypot' in cybersecurity speak, has different implementations and adaptations. Nevertheless, it's the process of exposing an asset like a computer server, network hardware, database etc., to the outside world, voluntarily without adequate threat protections, to view the incoming cyber threats, understand the techniques used, and to build a more secure enterprise cloud architecture.
In this paper, we focus more on Honeypot technique sourced cloud attack data, and using analytical approach, make sense of the raw-attack datasets, and predict future cyber-threat vectors and attack behavior.


```{r setup, include=FALSE, purl=FALSE, eval=TRUE}

source('R/ANLY502_GroupProjectData_Helper.R')

```

```{r echo=FALSE}

library(knitr)
library(printr)
library(formatR)
read_chunk('R/ANLY502_GroupProjectData_Chunks.R')

```

*Install the Required Libraries if not installed*
```{r installLibraries, echo=FALSE}
```

*Load the Required Libraries*
```{r loadLibraries, echo=FALSE}
```

Some [helper functions] do exists to support the code snippets below such as: ```loadSheetFromFile```

```{r helperFunctions, echo=FALSE}
```

#General Description of Data

The AWS Honeypot Database is an open-source database including information on cyber attacks/attempts.
Data has 451,581 data points collected from 9:53pm on 3 March 2013 to 5:55am on 8 September 2013.
The Data is in the CSV format with a size of ```47MB```, and is a ```6MB``` zipped download.
We will analyze this Data to identify any trends or correlations that could possibly be used in predictive cyber threat vectors.

---

Let's start by [Loading the Data Sheets]

```{r loadSheets, echo=FALSE, warning=FALSE}
```

*Structure of Data*

```{r}
str(HoneypotAttack) #Good way to quickly show the structure of something
```

*Description of Data*

```{r}
stat.desc(HoneypotAttack)
```

#List of explanatory variables

The explanatory variables are:	**src,	proto, type, spt, dpt, srcstr, cc, country, locale, localeabbr**

__src:__ the origin of the attack
__proto:__ the network protocol used during for the attack
__srcstr:__ the ip address of the attack origin
__cc:__ the country code
__country:__ the country of the origin of the attack
__locale:__ the locale of the origin of the attack
__localeabbr:__ the locale abbreviation of the origin of the attack

*Summary of Data*

```{r}
summary(HoneypotAttack)
```

Now let's [Adjust the Attacks Data]
```{r, attacksData, echo=FALSE}
```

## Attacks by Protocol

```{r protocolAttacks, echo=FALSE}
```

Then, let us [Adjust the Attacks Data]

```{r attacksData, echo=FALSE, warning=FALSE}
```

Then, let us [Setup the Mapping Data]

```{r mappingData, echo=FALSE, warning=FALSE}
```

Finally, let us [Plot the Attacks Data on the Map]

```{r mapPlots, echo=FALSE, warning=FALSE}
``` 

## Summary

This is work in progress. Still needed:

- Analyze attacks according to their time of occurence
- Analyze attacks according to US locations to check for important targets
- Create a model to predict next attack target and time

---

# Appendix:

### Required Libraries

```{r installLibraries, eval=FALSE}
```

```{r loadLibraries, eval=FALSE}
```

### Helper Functions

```{r helperFunctions, eval=FALSE}
```

### Loading the Data Sheets

```{r loadSheets, eval=FALSE}
```

### Adjust the Attacks Data

```{r attacksData, eval=FALSE}
```

### Setup the Mapping Data

```{r mappingData, eval=FALSE}
```

### Plot the Attacks Data on the Map

```{r mapPlots, eval=FALSE}
```

#Data Source

[Kaggle: AWS Honeypot Attack Data](https://www.kaggle.com/casimian2000/aws-honeypot-attack-data)
```
https://www.kaggle.com/casimian2000/aws-honeypot-attack-data
```

#Contributions

- #Akpany Aubin Ebby:
The personal contributions go here. Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
- #Amit Augustine: 
The personal contributions go here. Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
- #Zongxia Li:
The personal contributions go here. Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
