---
title: "ANLY 502 Group Project Report"
author:
 - "Akpany Benjamin Ebby"
 - "Amit Augustine"
 - "Zhongxia Li"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    highlight: zenburn
comment: Rmd Document with Markdown + Embedded R Code
---

#### Document as of `r Sys.Date()`

## Introduction

The world is moving fast towards a digital future, which encompasses people being Always On, Always Connected, and sharing a global network of information, as Data. Hence, we have the cloud revolution rapidly expanding in all spheres of our digital world, where all our information -self-created or even 3rd party sourced - is hosted and stored online in cyberspace. 
But, an often-overlooked factor in this cloud revolution and even transitional information processing and storage, was cybersecurity. 
Nowadays, there is tremendous focus on cybersecurity, due to risk of various security threats, amplified due to all the information stored online. We have various cybersecurity threat mitigation tools like vulnerability scanners, hybrid firewalls and Intrusion prevention systems, smart endpoint tools, honeypot techniques etc.
'Honeypot' in cybersecurity speak, has different implementations and adaptations. Nevertheless, it's the process of exposing an asset like a computer server, network hardware, database etc., to the outside world, voluntarily without adequate threat protections, to view the incoming cyber threats, understand the techniques used, and to build a more secure enterprise cloud architecture.
In this paper, we focus more on Honeypot technique sourced cloud attack data, and using analytical approach, make sense of the raw-attack datasets, and predict future cyber-threat vectors and attack behavior.


```{r setup, include=FALSE, purl=FALSE, eval=TRUE}

source('R/ANLY502_GroupProjectData_Helper.R')

```

```{r echo=FALSE}

library(knitr)
library(printr)
library(formatR)
read_chunk('R/ANLY502_GroupProjectData_Chunks.R')

```

*Install the Required Libraries if not installed*
```{r installLibraries, echo=FALSE}
```

*Load the Required Libraries*
```{r loadLibraries, echo=FALSE}
```

Some [helper functions] do exists to support the code snippets below such as: ```loadSheetFromFile```

```{r helperFunctions, echo=FALSE}
```

#General Description of Data

The AWS Honeypot Database is an open-source database including information on cyber attacks/attempts.
Data has 451,581 data points collected from 9:53pm on 3 March 2013 to 5:55am on 8 September 2013.
The Data is in the CSV format with a size of ```47MB```, and is a ```6MB``` zipped download.
We will analyze this Data to identify any trends or correlations that could possibly be used in predictive cyber threat vectors.

---

Let's start by [Loading the Data Sheets]

```{r loadSheets, echo=FALSE, warning=FALSE}
```

*Structure of Data*

```{r}
str(HoneypotAttack) #Good way to quickly show the structure of something
```

*Description of Data*

```{r}
stat.desc(HoneypotAttack)
```

*Summary of Data*

```{r}
summary(HoneypotAttack)
```

#List of explanatory variables

The explanatory variables are:	**src,	proto, type, spt, dpt, srcstr, cc, country, locale, localeabbr**

__src:__ the origin of the attack
__proto:__ the network protocol used during for the attack
__srcstr:__ the ip address of the attack origin
__cc:__ the country code
__country:__ the country of the origin of the attack
__locale:__ the locale of the origin of the attack
__localeabbr:__ the locale abbreviation of the origin of the attack

#Data Wrangling and Charts

Let's [Adjust the Attacks Data]
```{r, attacksData, echo=FALSE}
```

The [Attacks by Facet] give us a good idea about not only which protocols may be the most vulnerable,
but also which countries may be the most likely to launch a cyber attack.

```{r attacksByFacet, echo=FALSE}
```

Let us [Setup the Mapping Data]

```{r mappingData, echo=FALSE, warning=FALSE}
```

Finally, let us [Plot the Attacks Data on the Map] to have an idea of the location origins of cyber attack,
and provide an indication of their volume.

```{r mapPlots, echo=FALSE, warning=FALSE}
``` 

## Attacks according to US locations

The purpose of this section is to analyze the frequency of [attacks in each location in US]. Histogram is used to do the analysis.

```{r locationOfAttacks, echo=FALSE}
```
According to the histogram, the attacks occur in Orgon most frequently, following by US-East, and North California.

## Prediction of next attack time

One of the valuable information we want to know is when the next attack will occur. This section uses `forecast()` function to do the [time series prediction]. 

```{r forecastPrediction}
```
The plot shows the prediction of the time of the next 20 attacks.

According to the tables, the next attack will occur at 5.982467 which corresponding to 5:59 on 9/8/13. 

## Prediction of next attack location

Another valuable information we want to know is where the next attack will occur. This section uses `multinorm()` function to do the [location prediction]. Multinomial logistic regression is used to model nominal outcome variables, in which the log odds of the outcomes are modeled as a linear combination of the predictor variables. 

> summary(locationpred)
Call:
multinom(formula = host ~ src + spt + dpt, data = training)

Coefficients:
                    (Intercept)           src           spt           dpt
groucho-norcal    -3.078383e-18  5.820251e-12  2.504480e-14  1.470998e-14
groucho-oregon     5.813458e-18  5.698810e-10 -1.577155e-13 -1.196674e-14
groucho-sa        -3.302551e-18  1.990879e-11  4.004279e-14  2.046523e-14
groucho-singapore  2.093676e-18  4.507228e-10 -4.169394e-14 -7.025991e-15
groucho-sydney    -2.840168e-18 -2.014874e-12  4.869702e-14 -7.241270e-15
groucho-tokyo      1.069403e-17  5.387339e-10 -6.173720e-14 -3.467693e-14
groucho-us-east   -2.246735e-18  1.112273e-10  1.047060e-13  1.809391e-14
zeppo-norcal      -3.265972e-18  2.771078e-11  3.169074e-14  1.157041e-14

Std. Errors:
                   (Intercept)          src          spt          dpt
groucho-norcal    2.039262e-21 4.744180e-12 3.852650e-17 9.200814e-18
groucho-oregon    1.438330e-21 3.682128e-12 2.684050e-17 6.405141e-18
groucho-sa        2.010850e-21 4.698765e-12 3.796864e-17 9.067455e-18
groucho-singapore 1.491869e-21 3.802095e-12 2.783764e-17 6.646539e-18
groucho-sydney    2.055453e-21 4.769955e-12 3.884438e-17 9.276807e-18
groucho-tokyo     1.449455e-21 3.709682e-12 2.704207e-17 6.454545e-18
groucho-us-east   1.847278e-21 4.432439e-12 3.475929e-17 8.300355e-18
zeppo-norcal      1.995495e-21 4.674125e-12 3.766720e-17 8.995396e-18

Residual Deviance: 1319952 
AIC: 1320016

```{r locationPredictionPlot, echo=FALSE}
```

The prediction result shows the probability of the attack occuring at each locations. The attacklocationprob table shows the average probability of the attack occuring at each locations.

# Conclusion

We learned a few things from our analysis of the Honeypot Attacks Dataset:
- `TCP` is the most attacked, hence vulnerable internet protocol
- Most of the cyber attacks were launched from *China*
- The next attack and its location origin may be somewhat predicatable

---

# Appendix:

### Required Libraries

```{r installLibraries, eval=FALSE}
```

```{r loadLibraries, eval=FALSE}
```

### Helper Functions

```{r helperFunctions, eval=FALSE}
```

### Loading the Data Sheets

```{r loadSheets, eval=FALSE}
```

### Adjust the Attacks Data

```{r attacksData, eval=FALSE}
```

### Attacks by Facet
```{r attacksByFacet, eval=FALSE}
```

### attacks in each location in US
```{r locationOfAttacks, eval=FALSE}
```

### time series prediction
```{r forecastPrediction, eval=FALSE}
```

### location prediction

```{r locationPrediction, eval=FALSE}
```
```{r locationPredictionPlot, eval=FALSE}
```

### Setup the Mapping Data

```{r mappingData, eval=FALSE}
```

### Plot the Attacks Data on the Map

```{r mapPlots, eval=FALSE}
```

#Data Source

[Kaggle: AWS Honeypot Attack Data](https://www.kaggle.com/casimian2000/aws-honeypot-attack-data)
```
https://www.kaggle.com/casimian2000/aws-honeypot-attack-data
```

#Contributions

- #Akpany Aubin Ebby:
With my experience in Software Engineering, DevOps, as well as Data Visualization, I was able to make various contributions to this project, such as: setting up and managing the git repository that allowed use to share code, setting up the framework that allowed us to generate the report, and finally visually displaying interesting aspects of the Honeypot Attacks Dataset.
- #Amit Augustine: 
Due to my having experience and core knowledge in the fields on network security, cloud and threat landscape, I was able to understand and determine the various explanatory variables needed, help the team understand their relationships, and assist in the inference of our dataset analysis. Also involved in creating report and presentation slides.
- #Zhongxia Li:
With my experience with R, data analysis, and machine learning techniques, I was able to analyze the data set, including the exploratory data analysis and predictions. I contributed to the analysis of attacks’ location in US with histogram plot generated by R. I also worked on predicting the next attack time with time series forecast ,specifically ARIMA methodology. As well as possible target location prediction with Multinomial logistic regression method. I also involved in creating the report and presentation slides.
