---
title: "ANLY 502 Group Project Report"
author:
 - "Akpany Benjamin Ebby"
 - "Amit Augustine"
 - "Zongxia Li"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    highlight: zenburn
comment: Rmd Document with Markdown + Embedded R Code
---

#### Document as of `r Sys.Date()`

```{r setup, include=FALSE, purl=FALSE, eval=TRUE}

source('R/ANLY502_GroupProjectData_Helper.R')

```

```{r echo=FALSE}

library(knitr)
library(printr)
library(formatR)
read_chunk('R/ANLY502_GroupProjectData_Chunks.R')

```

*Install the Required Libraries if not installed*
```{r installLibraries, echo=FALSE}
```

*Load the Required Libraries*
```{r loadLibraries, echo=FALSE}
```

Some [helper functions] do exists to support the code snippets below such as: ```loadSheetFromFile```

```{r helperFunctions, echo=FALSE}
```

#General Description of Data

The AWS Honeypot Database is an open-source database including information on cyber attacks/attempts.
Data has 451,581 data points collected from 9:53pm on 3 March 2013 to 5:55am on 8 September 2013.
The Data is in the CSV format with a size of ```47MB```, and is a ```6MB``` zipped download.
We will analyze this Data to identify any trends or correlations that could possibly be used in predictive cyber threat vectors.

---

Let's start by [Loading the Data Sheets]

```{r loadSheets, echo=FALSE, warning=FALSE}
```

*Structure of Data*

```{r}
str(HoneypotAttack) #Good way to quickly show the structure of something
```

*Description of Data*

```{r}
stat.desc(HoneypotAttack)
```

#List of explanatory variables

The explanatory variables are:	**src,	proto, type, spt, dpt, srcstr, cc, country, locale, localeabbr**

__src:__ the origin of the attack
__proto:__ the network protocol used during for the attack
__srcstr:__ the ip address of the attack origin
__cc:__ the country code
__country:__ the country of the origin of the attack
__locale:__ the locale of the origin of the attack
__localeabbr:__ the locale abbreviation of the origin of the attack

*Summary of Data*

```{r}
summary(HoneypotAttack)
```

Now let's [Adjust the Attacks Data]
```{r, attacksData, echo=FALSE}
```

## Attacks by Protocol

```{r protocolAttacks, echo=FALSE}
```

Then, let us [Adjust the Attacks Data]

```{r attacksData, echo=FALSE, warning=FALSE}
```

Then, let us [Setup the Mapping Data]

```{r mappingData, echo=FALSE, warning=FALSE}
```

Finally, let us [Plot the Attacks Data on the Map]

```{r mapPlots, echo=FALSE, warning=FALSE}
``` 

## Summary

This is work in progress. Still needed:

- Analyze attacks according to their time of occurence
- Analyze attacks according to US locations to check for important targets
- Create a model to predict next attack target and time

---

# Appendix:

### Required Libraries

```{r installLibraries, eval=FALSE}
```

```{r loadLibraries, eval=FALSE}
```

### Helper Functions

```{r helperFunctions, eval=FALSE}
```

### Loading the Data Sheets

```{r loadSheets, eval=FALSE}
```

### Adjust the Attacks Data

```{r attacksData, eval=FALSE}
```

### Setup the Mapping Data

```{r mappingData, eval=FALSE}
```

### Plot the Attacks Data on the Map

```{r mapPlots, eval=FALSE}
```

#Data Source

[Kaggle: AWS Honeypot Attack Data](https://www.kaggle.com/casimian2000/aws-honeypot-attack-data)
```
https://www.kaggle.com/casimian2000/aws-honeypot-attack-data
```
