---
title: "ANLY 500-53 Laboratory #1 Report"
author:
- name: Akpany Benjamin Ebby
  affiliation: Harrisburg University of Science and Technology (Master of Science in Analytics)
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    highlight: tango
    toc: true
    toc_depth: 2
    number_sections: false
    fig_width: 7
    fig_height: 6
    fig_caption: true
    template: resources/svm-latex-ms.tex
comment: Rmd Document with Markdown + Embedded R Code
bibliography: resources/biblio.bib
biblio-style: "apalike"
link-citations: true
---
\fontsize{8}{11}
\fontseries{b}
\selectfont
\sffamily

## Disclaimer:
This Lab Report #1 was last generated `r format(Sys.time(), '%B %d, %Y')`. It is based on the Business Analytics textbook excercises [@BusinessAnalytics_2016] and the R Mardown documentation [@Bookdown_2018]. In addition, [Required Libraries] and [Helper Functions] will be used in support of the various code snippets throughout the document.

```{r setup, include=FALSE, purl=FALSE, eval=TRUE}

source('R/ANLY500_Lab1_Helper.R')
source('R/ANLY500_Lab1_Chunks.R')

```

```{r echo=FALSE}

library(knitr)
library(printr)
library(formatR)
read_chunk('R/ANLY500_Lab1_Chunks.R')

```

#Chapter 1:

As you may have seen in text book, Mrs. Bruke, your client has provided the dataset for you (excel file). To prepare for this task,
you have decided to review each worksheet and determine whether the data were gathered from internal sources, external sources,
or have been generated from special studies. Also, you need to know whether the measures are categorical, ordinal, interval, or ratio.
Prepare a report summarizing the characteristics of the metrics used in each worksheet.

We start by [Loading the Data Sheets].

* Dealer Satisfaction:
1. *Region:* Categorical
3. *Year:* Ordinal
4. *L0:* Ordinal
5. *L1:* Ordinal
6. *L2:* Ordinal
7. *L3:* Ordinal
8. *L4:* Ordinal
9. *L5:* Ordinal
10. *SampleSize:* Numerical

* End-User Satisfaction:
1. *Region:* Categorical
3. *Year:* Ordinal
4. *L0:* Ordinal
5. *L1:* Ordinal
6. *L2:* Ordinal
7. *L3:* Ordinal
8. *L4:* Ordinal
9. *L5:* Ordinal
10. *SampleSize:* Numerical

* 2014 Customer Survey:
1. *Region:* Categorical
2. *Quality:* Ordinal
3. *Ease of Use:* Interval
4. *Price:* Ordinal
5. *Service:* Ordinal

* Complaints:
1. *Month:* Ordinal
2. *World:* Categorical
3. *NA:* Categorical
4. *SA:* Categorical
5. *Eur:* Categorical
6. *Pac:* Categorical
7. *China:* Categorical

* Mower Unit Sales:
1. *Month:* Ordinal
2. *NA:* Categorical
3. *SA:* Categorical
4. *Europe:* Categorical
5. *Pacific:* Categorical
6. *China:* Categorical
7. *World:* Categorical

* Tractor Unit Sales:
1. *Month:* Ordinal
2. *NA:* Categorical
3. *SA:* Categorical
4. *Eur:* Categorical
5. *Pac:* Categorical
6. *China:* Categorical
7. *World:* Categorical

* Industry Mower Total Sales:
1. *Month:* Ordinal
2. *NA:* Categorical
3. *SA:* Categorical
4. *Eur:* Categorical
5. *Pac:* Categorical
6. *China:* Categorical
7. *World:* Categorical

* Industry Tractor Total Sales:
1. *Month:* Ordinal
2. *NA:* Categorical
3. *SA:* Categorical
4. *Eur:* Categorical
5. *Pac:* Categorical
6. *China:* Categorical
7. *World:* Categorical

* Unit Production Costs:
1. *Month:* Ordinal
2. *Tractor:* Numerical Continuous
3. *Mower:* Numerical Continuous

* Operating and Interest Expenses:
1. *Month:* Ordinal
2. *Administrative:* Numerical Continuous
3. *Depreciation:* Numerical Continuous
4. *Interest:* Numerical Continuous

* On-Time Delivery:
1. *Month:* Ordinal
2. *Number of deliveries:* Numerical Discrete
3. *Number On Time:* Numerical Discrete
4. *Percent:* Numerical Continuous

* Defects After Delivery:
1. *Month:* Ordinal
2. *2010:* Numerical Discrete
3. *2011:* Numerical Discrete
4. *2012:* Numerical Discrete
5. *2013:* Numerical Discrete
6. *2014:* Numerical Discrete

* Time to Pay Suppliers:
1. *Month:* Ordinal
2. *Working Days:* Numerical Continuous

* Response times to customer service calls:
1. *Q1 2013:* Numerical Continuous
2. *Q2 2013:* Numerical Continuous
3. *Q3 2013:* Numerical Continuous
4. *Q4 2013:* Numerical Continuous
5. *Q1 2014:* Numerical Continuous
6. *Q2 2014:* Numerical Continuous
7. *Q3 2014:* Numerical Continuous
8. *Q4 2014:* Numerical Continuous

* Employee Satisfaction Results:
1. *Quarter:* Ordinal
2. *Production:* Numerical Continuous
3. *Sample size:* Numerical Discrete
4. *Manager:* Numerical Continuous
5. *Sample size:* Numerical Discrete
6. *Administration:* Numerical Continuous
7. *Sample size:* Numerical Discrete
8. *Total:* Numerical Continuous
9. *Sample size:* Numerical Discrete

* Engine Production Time:
1. *Sample:* Numerical Discrete
2. *Production Time (min):* Numerical Continuous

* Unit Tractor Transmission Costs:
1. *Current:* Numerical Continuous
2. *Process A:* Numerical Continuous
3. *Process B:* Numerical Continuous

* Blade Weight:
1. *Sample:* Numerical Discrete
2. *Weight:* Numerical Continuous

* Mower Test Functional Performance:
1. *Observation:* Numerical Discrete
2. *1:* Categorical
3. *2:* Categorical
4. *3:* Categorical
5. *4:* Categorical
6. *5:* Categorical
7. *6:* Categorical
8. *7:* Categorical
9. *8:* Categorical
10. *9:* Categorical
11. *10:* Categorical
12. *11:* Categorical
13. *12:* Categorical
14. *13:* Categorical
15. *14:* Categorical
16. *15:* Categorical
17. *16:* Categorical
18. *17:* Categorical
19. *18:* Categorical
20. *19:* Categorical
21. *20:* Categorical
22. *21:* Categorical
23. *22:* Categorical
24. *23:* Categorical
25. *24:* Categorical
26. *25:* Categorical
27. *26:* Categorical
28. *27:* Categorical
29. *28:* Categorical
30. *29:* Categorical
31. *30:* Categorical

* Employee Retention:
1. *YearsPLE:* Numerical Continuous
2. *YrsEducation:* Numerical Discrete
3. *College GPA:* Numerical Continuous
4. *Age:* Numerical Discrete
5. *Gender:* Categorical
6. *College Grad:* Categorical
7. *Local:* Categorical

* Unit Shipping Cost:
1. *Plant:* Categorical
2. *Customer:* Categorical
3. *Mowers:* Numerical Continuous
4. *Tractors:* Numerical Continuous

* Fixed Costs of Capacity Increase or New Construction:
1. *Current Plants:* Categorical
2. *PlantType:* Categorical
3. *CapacityAmount:* Numerical Discrete
4. *Cost:* Numerical Continuous

* Purchasing Survey:
1. *Delivery speed:* Numerical Continuous
1. *Price level:* Numerical Continuous
1. *Price flexibility:* Numerical Continuous
1. *Manufacturing image:* Numerical Continuous
1. *Overall service:* Numerical Continuous
1. *Salesforce image:* Numerical Continuous
1. *Product quality:* Numerical Continuous
1. *Usage Level:* Numerical Discrete
1. *Satisfaction Level:* Numerical Continuous
1. *Size of firm:* Categorical
1. *Purchasing Structure:* Categorical
1. *Industry:* Categorical
1. *Buying Type:* Categorical

#Chapter 3:

##Part 1:

PLE originally produced lawn mowers, but a significant portion of sales volume over recent years has come from the growing small-tractor market.
As we noted in the case in Chapter 1, PLE sells their products worldwide, with sales regions including North America, South America, Europe, and the Pacific Rim.
Three years ago a new region was opened to serve China, where a booming market for small tractors has been established.
PLE has always emphasized quality and considers the quality it builds into its products as its primary selling point.
In the past 2 years, PLE has also emphasized the ease of use of their products.
Before digging into the details of operations, Elizabeth Burke wants to gain an overview of PLE’s overall business performance and market position by examining the information provided in the database. Specifically, she is asking you to construct appropriate charts for the data in the following worksheets and summarize your conclusions from analysis of these charts.

1. Dealer Satisfaction
2. End-User Satisfaction
3. Complaints
4. Mower Unit Sales
5. Tractor Unit Sales
6. On-Time Delivery
7. Defects after Delivery
8. Response Time

### Step 1 (Dealer Satisfaction)

The Data Structure of the Dealer Satisfaction, End-User Satisfaction, Complaints, Mower Unit Sales, Tractor Unit Sales, On-Time Delivery, Defects after Delivery, Response Time
Excel Sheets is as follows:

```{r}

str(DealerSat)
str(EndUserSat)
str(Complaints)
str(MowerUnitSales)
str(TractorUnitSales)
str(OnTimeDelivery)
str(DefectsAfterDelivery)
str(ResponseTimesCSC)

```


The [Dealer Satisfaction by Region] is as follows:

```{r satisfactionByRegionAxis, echo=FALSE}
```

*North America:*

```{r dealerSatNorthAmerica, echo=FALSE}
```

*South America:*

```{r dealerSatSouthAmerica, echo=FALSE}
```

*Europe:*

```{r dealerSatEurope, echo=FALSE}
```

*Pacific Rim:*

```{r dealerSatPacificRim, echo=FALSE}
```

*China:*

```{r dealerSatChina, echo=FALSE}
```


### Step 2 (End-User Satisfaction)

The [End-User Satisfaction by Region] is as follows:

*North America:*

```{r endUserSatNorthAmerica, echo=FALSE}
```

*South America:*

```{r endUserSatSouthAmerica, echo=FALSE}
```

*Europe:*

```{r endUserSatEurope, echo=FALSE}
```

*Pacific Rim:*

```{r endUserSatPacificRim, echo=FALSE}
```

*China:*

```{r endUserSatChina, echo=FALSE}
```

### Step 3: (Complaints)

```{r echo=FALSE}

plot(Complaints$World, ylim=range(c(0, 400)), type="l", xlab="Month", ylab="Number of Complaints")
par(new=TRUE)
plot(Complaints$'NA', ylim=range(c(0,400)), type="l", col="red", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)
plot(Complaints$SA, ylim=range(c(0,400)), type="l", col="green", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)
plot(Complaints$Eur, ylim=range(c(0,400)), type="l", col="blue", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)
plot(Complaints$Pac, ylim=range(c(0,400)), type="l", col="magenta", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)
plot(Complaints$China, ylim=range(c(0,400)), type="l", col="deeppink4", axes = FALSE, xlab = "", ylab = "")

```

### Step 4: (Mower Unit Sales)

The [Mower Unit Sales by Year] is as follows:

*2010:*

```{r mowerUnitSales2010, echo=FALSE}
```

*2011:*

```{r mowerUnitSales2011, echo=FALSE}
```

*2012:*

```{r mowerUnitSales2012, echo=FALSE}
```

*2013:*

```{r mowerUnitSales2013, echo=FALSE}
```

*2014:*

```{r mowerUnitSales2014, echo=FALSE}
```

### Step 5: (Tractor Unit Sales)

The [Tractor Unit Sales by Year] is as follows:

*2010:*

```{r tractorUnitSales2010, echo=FALSE}
```

*2011:*

```{r tractorUnitSales2011, echo=FALSE}
```

*2012:*

```{r tractorUnitSales2012, echo=FALSE}
```

*2013:*

```{r tractorUnitSales2013, echo=FALSE}
```

*2014:*

```{r tractorUnitSales2014, echo=FALSE}
```

### Step 6: (On-Time Delivery)

```{r}

ggplot(OnTimeDelivery, aes(x=Month, y=Percent)) + geom_point(color='blue') + scale_y_continuous(labels = percent_format()) + geom_smooth(method = "lm", color='red')

```

### Step 7: (Defects after Delivery)

```{r}

plot(DefectsAfterDelivery$`2010`, ylim=range(c(0, 900)), type="l", xlab="Month", ylab="Number of Defects")
par(new=TRUE)
plot(DefectsAfterDelivery$`2011`, ylim=range(c(0, 900)), type="l", col="blue", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)
plot(DefectsAfterDelivery$`2013`, ylim=range(c(0, 900)), type="l", col="green", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)
plot(DefectsAfterDelivery$`2014`, ylim=range(c(0, 900)), type="l", col="red", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)

```

### Step 8: (Response Time)

*2013:*

```{r}

plot(ResponseTimesCSC$`Q1 2013`, ylim=range(c(0, 10)), type="l", xlab="", ylab="Number of Defects")
par(new=TRUE)

plot(ResponseTimesCSC$`Q2 2013`, ylim=range(c(0, 10)), type="l", col="blue", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)
plot(ResponseTimesCSC$`Q3 2013`, ylim=range(c(0, 10)), type="l", col="green", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)
plot(ResponseTimesCSC$`Q4 2013`, ylim=range(c(0, 10)), type="l", col="red", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)

```

*2014:*

```{r}

plot(ResponseTimesCSC$`Q1 2014`, ylim=range(c(0, 10)), type="l", xlab="", ylab="Number of Defects")
par(new=TRUE)
plot(ResponseTimesCSC$`Q2 2014`, ylim=range(c(0, 10)), type="l", col="blue", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)
plot(ResponseTimesCSC$`Q3 2014`, ylim=range(c(0, 10)), type="l", col="green", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)
plot(ResponseTimesCSC$`Q4 2014`, ylim=range(c(0, 10)), type="l", col="red", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)

```

//TODO: Plot the REST!!!!
------------------------

##Part 2:

As noted in the case in Chapter 1, the supply chain worksheets provide cost data associated with logistics between existing plants and customers as well as proposed new plants. Ms. Burke wants you to extract the records associated with the unit shipping costs of proposed plant locations and compare the costs of existing locations against those of the proposed locations using quartiles.

*Unit Shipping Cost:*

```{r}

str(UnitShippingCost)

summary(UnitShippingCost)

```

*Unit Shipping Cost for Mowers:*

```{r}

summary(UnitShippingCost$Mowers)

hist(UnitShippingCost$Mowers, xlab="Shipping Cost in $")

```

*Unit Shipping Cost for Tractors:*

```{r}

summary(UnitShippingCost$Tractors)

hist(UnitShippingCost$Tractors, xlab="Shipping Cost in $")

```

##Part 3:

Ms. Burke would also like a quantitative summary of the average responses for each of the customer attributes in the worksheet 2014 Customer Survey for each market region as a cross-tabulation (use PivotTables as appropriate), along with frequency distributions, histograms, and quartiles of these data.

```{r}

str(CustomerSurvey2014)
summary(CustomerSurvey2014)

str(CustomerSurvey2014)

barplot(table(CustomerSurvey2014$Region))

hist(CustomerSurvey2014$Quality, main="Quality - Number of Responses", xlab="Level of Quality")

```

##Part 4:

Propose a monthly dashboard of the most important business information that Ms. Burke can use on a routine basis as data are updated. Create one using the most recent data. Your dashboard should not consist of more than 6–8 charts, which should fit comfortably on one screen.

//TODO: Do this part as you best see fit in terms of a choice of a dashboard
------------------------------------------------------------------------------

#Chapter 4:

Your client wants some detailed statistical information about much of the data in the PLE database. In particular, she wants to know the following:

1. the mean satisfaction ratings and standard deviations by year and region in the worksheets Dealer Satisfaction and End-User Satisfaction
2. a descriptive statistical summary for the 2012 customer survey data
3. how the response times differ in each quarter of the worksheet Response Time
4. how defects after delivery (worksheet Defects after Delivery) have changed over these 5 years
How sales of mowers and tractors compare with industry totals and how strongly monthly product sales are correlated with industry sales

#Chapter 5:

PLE collects a variety of data from special studies, many of which are related to the quality of its products. The company collects data about functional test performance of its mowers after assembly; results from the past 30 days are given in the worksheet Mower Test. In addition, many in-process measurements are taken to ensure that manufacturing processes remain in control and can produce according to design specifications. The worksheet Blade Weight shows 350 measurements of blade weights taken from the manufacturing process that produces mower blades during the most recent shift. Elizabeth Burke has asked you to study these data from an analytics perspective. Drawing upon your experience, you have developed a number of questions.

1. For the mower test data, what distribution might be appropriate to model the failure of an individual mower?

A **Bernoulli Distribution** would be most appropriate.

2. What fraction of mowers fails the functional performance test using all the mower test data?

```{r}

countFail <- length(which(MowerTest == "Fail"))
countFail

```

So there are 54 “Fail” in the MowerTest data set, or the fraction of “Fail”, i.e. the probability of “Fail” is 54/3000 = 0.018.

3. What is the probability of having x failures in the next 100 mowers tested, for x from 0 to 20?

```{r}

y <- dbinom(0:20, 100, .018)
y
plot(y)

```

4. What is the average blade weight and how much variability is occurring in the measurements of blade weights?

```{r echo=FALSE}
```

```{r}

#View(BladeWeight)
str(BladeWeight)

(sum(BladeWeight$Weight)/350)
sd(BladeWeight$Weight)

```

5. Assuming that the data are normal, what is the probability that blade weights from this process will exceed 5.20?

```{r}

y = pnorm(5.20, mean=4.99, sd=0.11)
y
1 - y

```

6. What is the probability that weights will be less than 4.80?

```{r}

pnorm(4.80, mean=4.99, sd=0.11)

```

7. What is the actual percent of weights that exceed 5.20 or are less than 4.80 from the data in the worksheet?

```{r}

countblade <- length(which(BladeWeight$Weight > 5.20))
countblade
countblade2 <- length(which(BladeWeight$Weight <= 4.80))
countblade2

```

8. Is the process that makes the blades stable over time? That is, are there any apparent changes in the pattern of the blade weights?

```{r}

plot(BladeWeight$Sample, BladeWeight$Weight)

```

9. Could any of the blade weights be considered outliers, which might indicate a problem with the manufacturing process or materials?

Looking at the scatter plot, only close to the 200th blade was there any trouble.  It isn’t too much trouble to find that this is blade #171.

10. Was the assumption that blade weights are normally distributed justified? What is the best-fitting probability distribution for the data?

```{r}

hist(BladeWeight$Weight)

```

#Chapter 6:

In reviewing your previous reports, several questions came to Elizabeth Burke’s mind. Use point and interval estimates to help answer these questions.

1. What proportion of customer’s rate the company with “top box” survey responses (which is defined as scale levels 4 and 5) on quality, ease of use, price, and service in the 2014 Customer Survey worksheet? How do these proportions differ by geographic region?

```{r}

countByRegion <- table(CustomerSurvey2014$Region, CustomerSurvey2014$Quality)
countByRegion

sum(countByRegion[3,4], countByRegion[3,5])

```

2. What estimates, with reasonable assurance, can PLE give customers for response times to customer service calls?

Q1

````{r}

Q1.13mean <- mean(ResponseTimesCSC$'Q1 2013')
Q1.13std <- sd(ResponseTimesCSC$'Q1 2013')

Q1.13mean
Q1.13std

z.test(ResponseTimesCSC$'Q1 2013', sigma.x = Q1.13std)

```

Q2

````{r}

Q2.13mean <- mean(ResponseTimesCSC$'Q2 2013')
Q2.13std <- sd(ResponseTimesCSC$'Q2 2013')
z.test(ResponseTimesCSC$'Q2 2013', sigma.x = Q2.13std)

````

3. Engineering has collected data on alternative process costs for building transmissions in the worksheet Transmission Costs. Can you determine whether one of the proposed processes is better than the current process?

```{r}

current.sd <- sd(TransmissionCosts$Current)
z.test(TransmissionCosts$Current, sigma.x = current.sd)

```

4. What would be a confidence interval for an additional sample of mower test performance as in the worksheet Mower Test?

\begin{equation}
Standard\hspace{1 mm}deviation = \sqrt{\frac{mean * (1 - mean)}{n}}
\end{equation}

```{r warn=FALSE}

A <- data.frame(lapply(MowerTest, function(x) as.numeric(x)))
str(A)
A[,5] <- 2
A[,10] <- 2
A[,27] <- 2
A[,30] <- 2
str(A)

B <- data.matrix(A[,-1])
str(B)
B <- B - 1
str(B)

B <- B - 1
length(which(B==0))
1-mean(B)
t.test(B, mu=0.982)

hist(BladeWeight$Weight)

```

The standard error of the mean for our blade weight data can be found using

```{r}

sem <- sd(BladeWeight$Weight)/sqrt(length(BladeWeight$Weight))
sem

A <- lm(BladeWeight$Weight~ ., BladeWeight)
str(A)
plot(A)

```

5. For the data in the worksheet Blade Weight, what is the sampling distribution of the mean, the overall mean, and the standard error of the mean? Is a normal distribution an appropriate assumption for the sampling distribution of the mean?
6. How many blade weights must be measured to find a 95% confidence interval for the mean blade weight with a sampling error of at most 0.2? What if the sampling error is specified as 0.1?

#Chapter 7:

1. Are there significant differences in ratings of specific product/service attributes in the 2014 Customer Survey worksheet?

```{r}

Quality <- CustomerSurvey2014$Quality
str(CustomerSurvey2014)
Ease.of.Use <- CustomerSurvey2014$'Ease of Use'
Price <- CustomerSurvey2014$Price
Service <- CustomerSurvey2014$Service

Data <- data.frame(Y=c(Quality, Ease.of.Use, Price, Service), Para=factor(rep(c("Quality", "Ease.of.Use", "Price", "Service"), times=c(length(Quality), length(Ease.of.Use), length(Price), length(Service)))))
str(Data)

fm1 <- aov(Y~Para, data = Data)
anova(fm1)

```

2. In the worksheet On-Time Delivery, has the proportion of on-time deliveries in 2014 significantly improved since 2010?

```{r}

p0 <- sum(OnTimeDelivery$'Number On Time'[1:12]/sum(OnTimeDelivery$'Number of deliveries'[1:12]))
p0

pbar <- sum(OnTimeDelivery$'Number On Time'[49:60])/sum(OnTimeDelivery$'Number of deliveries'[49:60])
pbar

n <- 12
z <- (pbar - p0)/sqrt(p0*(1-p0)/n)
z

alpha <- 0.05
z.alpha <- qnorm(1 - alpha)
z.alpha

pval <- pnorm(z, lower.tail = FALSE)
pval

```

3. Have the data in the worksheet Defects After Delivery changed significantly over the past 5 years?

```{r}

sum(DefectsAfterDelivery$'2014')/12

defects.by.year <- c(826.33, 837.42, 785.92, 669.08, 496.25)
plot(defects.by.year, type="b", lwd=2)

a <- DefectsAfterDelivery$'2010'
b <- DefectsAfterDelivery$'2014'
t.test(a,b, var.equal = FALSE, paired = FALSE)

```

4. Although engineering has collected data on alternative process costs for building transmissions in the worksheet Transmission Costs, why didn’t they reach a conclusion as to whether one of the proposed processes is better than the current process?

```{r}

t.test(TransmissionCosts$Current, TransmissionCosts$'Process A', var.equal = FALSE, paired = FALSE)
t.test(TransmissionCosts$Current, TransmissionCosts$'Process B', var.equal = FALSE, paired = FALSE)

```

5. Are there differences in employee retention due to gender, college graduation status, or whether the employee is from the local area in the data in the worksheet Employee Retention?

```{r}

gender <- EmployeeRetention$Gender
yearsPLE <- EmployeeRetention$YearsPLE
male.female <- data.frame(gender=gender, yearsPLE=yearsPLE)

male.female[order(male.female$gender),]
t.test(male.female$yearsPLE ~ male.female$gender, var.equal = FALSE, paired = FALSE)

```

Once again, the p-value is greater than .05 who we conclude that there is no statistically significant difference between men and women in terms of the number of years of service at PLE.

# Appendix:

### Required Libraries

```{r installLibraries, eval=FALSE}
```

```{r loadLibraries, eval=FALSE}
```

### Helper Functions

```{r helperFunctions, eval=FALSE}
```

### Loading the Data Sheets

```{r loadSheets, eval=FALSE}
```

### Dealer Satisfaction by Region

```{r satisfactionByRegionAxis, eval=FALSE}
```

*North America:*

```{r dealerSatNorthAmerica, eval=FALSE}
```

*South America:*

```{r dealerSatSouthAmerica, eval=FALSE}
```

*Europe:*

```{r dealerSatEurope, eval=FALSE}
```

*Pacific Rim:*

```{r dealerSatPacificRim, eval=FALSE}
```

*China:*

```{r dealerSatChina, eval=FALSE}
```

### End-User Satisfaction by Region

*North America:*

```{r endUserSatNorthAmerica, eval=FALSE}
```

*South America:*

```{r endUserSatSouthAmerica, eval=FALSE}
```

*Europe:*

```{r endUserSatEurope, eval=FALSE}
```

*Pacific Rim:*

```{r endUserSatPacificRim, eval=FALSE}
```

*China:*

```{r endUserSatChina, eval=FALSE}
```

### Mower Unit Sales by Year

*2010:*

```{r mowerUnitSales2010, eval=FALSE}
```

*2011:*

```{r mowerUnitSales2011, eval=FALSE}
```

*2012:*

```{r mowerUnitSales2012, eval=FALSE}
```

*2013:*

```{r mowerUnitSales2013, eval=FALSE}
```

*2014:*

```{r mowerUnitSales2014, eval=FALSE}
```

### Tractor Unit Sales by Year

*2010:*

```{r tractorUnitSales2010, eval=FALSE}
```

*2011:*

```{r tractorUnitSales2011, eval=FALSE}
```

*2012:*

```{r tractorUnitSales2012, eval=FALSE}
```

*2013:*

```{r tractorUnitSales2013, eval=FALSE}
```

*2014:*

```{r tractorUnitSales2014, eval=FALSE}
```

# References:



