---
title: "ANLY 500 Lab 1"
author:
- name: Akpany Benjamin Ebby
  affiliation: Harrisburg University of Science and Technology (Master of Science in Analytics)
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    highlight: tango
    toc: true
    toc_depth: 2
    number_sections: false
    fig_width: 7
    fig_height: 6
    fig_caption: true
    template: resources/svm-latex-ms.tex
comment: Rmd Document with Markdown + Embedded R Code
bibliography: resources/biblio.bib
biblio-style: "apalike"
link-citations: true
---
\fontsize{8}{11}
\fontseries{b}
\selectfont
\sffamily

## Lab 1 Report as of `r format(Sys.time(), '%B %d, %Y')` based on the Business Analytics textbook excercises (@BusinessAnalytics_2016) and the R Mardown documentation (@Bookdown_2018)

```{r setup, include=FALSE, purl=FALSE, eval=TRUE}

source('R/ANLY500_Lab1_Helper.R')

```

```{r echo=FALSE}

library(knitr)
library(printr)
library(formatR)
read_chunk('R/ANLY500_Lab1_Chunks.R')

```

*Install the Required Libraries if not installed*
```{r installLibraries}
```

*Load the Required Libraries*
```{r echo=FALSE}

library(readxl)
library(ggplot2)
library(psych)
library(Hmisc)
library(stats)
library(pastecs)
library(magrittr)
library(reshape2)
library(BSDA)

```

The following helper functions will be used in support of the code snippets throughout the document:
```{r helperFunctions}
```

#Chapter 1

###*Set Data File Name:*

```{r}

perfFileName <- "Performance Lawn Equipment Database.xlsx"

```

###*Dealer Satisfaction Sheet*

```{r}

# Dealer Satisfaction
DealerSat <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = " Dealer Satisfaction", skip = 1) #Skip 1 skips the first row
str(DealerSat) #Good way to quickly show the structure of something
#summary(DealerSat)
#head(DealerSat)
#stat.desc(DealerSat)
#View(DealerSat)

```

###*End-User Satisfaction*

```{r}

#Method 1 - Remove Rows from the top section if a dataframe. use the skip = function
EndUserSat <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "End-User Satisfaction", skip = 1)
str(EndUserSat)
#View(EndUserSat)

#Method 2 - Remove Rows

```

###*2014 Customer Survey Sheet:*

```{r}

CustomerSurvey2014 <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "2014 Customer Survey", skip = 1)
str(CustomerSurvey2014)

```

###*Complaints Sheet:*

```{r}

Complaints <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Complaints", skip = 1)
str(Complaints)

```

###*Mower Unit Sales Sheet:*

```{r}

MowerUnitSales <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Mower Unit Sales", skip = 1)
str(MowerUnitSales)

```

###*Tractor Unit Sales Sheet:*

```{r}

TractorUnitSales <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Tractor Unit Sales", skip = 1)
str(TractorUnitSales)

```

###*Industry Mower Total Sales Sheet:*

```{r}

IndustryMowerTotalSales <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Industry Mower Total Sales", skip = 1)
str(IndustryMowerTotalSales)

```

###*Industry Tractor Total Sheet:*

```{r}

IndustryTractorTotalSales <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Industry Tractor Total Sales", skip = 1)
str(IndustryTractorTotalSales)

```

###*Unit Production Costs Sheet:*

```{r}

UnitProductionCosts <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Unit Production Costs", skip = 1)
str(UnitProductionCosts)

```

###*Operating & Interest Expenses Sheet:*

```{r}

OperatingAndInterestExpenses <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Operating & Interest Expenses", skip = 1)
str(OperatingAndInterestExpenses)

```

###*On-Time Delivery Sheet:*

```{r}

OnTimeDelivery <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "On-Time Delivery", skip = 1)
str(OnTimeDelivery)

```

###*Defects After Delivery Sheet:*

```{r}

DefectsAfterDelivery <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Defects After Delivery", skip = 1)
str(DefectsAfterDelivery)

```

###*Time to Pay Suppliers Sheet:*

```{r}

TimeToPaySuppliers <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Time to Pay Suppliers", skip = 1)
str(TimeToPaySuppliers)

```

###*Response times to customer service calls Sheet:*

```{r}

ResponseTimesCSC <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Response Time", skip = 1)
str(ResponseTimesCSC)

```

###*Employee Satisfaction Results Sheet:*

```{r}

EmployeeSatisfaction <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Employee Satisfaction", skip = 1)
str(EmployeeSatisfaction)

```

###*Engine Production Time Sheet:*

```{r}

EngineProductionTime <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Engines", skip = 1)
str(EngineProductionTime)

```

###*Unit Tractor Transmission Costs Sheet:*

```{r}

TransmissionCosts <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Transmission Costs", skip = 1)
str(TransmissionCosts)

```

###*Blade Weight Sheet:*

```{r}

BladeWeight <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Blade Weight")
str(BladeWeight)
#View(BladeWeight)

```

###*Mower Test Functional Performance Sheet:*

```{r}

MowerTest <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Mower Test", skip = 1)
str(MowerTest)

```

###*Employee Retention Sheet:*

```{r}

EmployeeRetention <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Employee Retention", skip = 1)
str(EmployeeRetention)

```

###*Unit Shipping Cost Sheet:*

```{r}

UnitShippingCost <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Shipping Cost", skip = 1)
str(UnitShippingCost)

```

###*Fixed Costs of Capacity Increase or New Construction Sheet:*

```{r}

FixedCost <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Fixed Cost", skip = 1)
str(FixedCost)

```

###*Purchasing Survey Sheet:*

```{r}

PurchasingSurvey <- perfFileName %>%
    fullFilePath %>%
    read_excel(sheet = "Purchasing Survey", skip = 1)
str(PurchasingSurvey)

```

#Chapter 2

### Step 1

```{r}

y2010 <- DealerSat[ which(DealerSat$Year == 2010), ]
y2010

y2010L0 <- sum(y2010[,3])
y2010L0

```

### Step 2

```{r}

y <- t(sapply(MowerTest[-1], function(x) table(factor(x, levels=c("Pass", "Fail")))))
y

y2 <- as.data.frame(y)
y2
str(y2)
sum(y2$Fail)
sum(y2$Pass)

```

### Step 3

```{r}

str(MowerUnitSales)
summary(MowerUnitSales)

str(TractorUnitSales)
summary(TractorUnitSales)

## Where is the Prices data coming from?

str(UnitProductionCosts)
summary(UnitProductionCosts)

# Maybe
Prices <- UnitProductionCosts

str(Prices)
summary(Prices)

## Prices
## Prices[1:2]
## Prices[1:12,2]
## Prices[1,2]
## Prices[1:1,2:1]

## mowerRev2010 <- MowerUnitSales[1:12, 3:7] * Prices[1:12,2]

## tractorPrice <- Prices[1,2]
## tractorPrice
## MowerUnitSales[1:12, 3:7] * tractorPrice

Prices$Tractor[1]
MowerUnitSales[1:12, 3:7] * Prices$Tractor[1]
MowerUnitSales[1:12, 3:7] * Prices$Tractor[1:12]

#mowerRev2010 <- MowerUnitSales[1:12, 3:8] * Prices[1,2] # ????
#mowerRev2010

```

### Step 4

apply the sum function to find the market share of both the Mower and Tractor

#Chapter 3

## Part 1

You have been tasked with putting together an overview of PLE’s business performance and market position.  You have specifically been asked to construct appropriate charts and summarize your conclusions for:
a.	Dealer Satisfaction
b.	End-User Satisfaction
c.	Complaints
d.	Mower Unit Sales
e.	Tractor Unit Sales
f.	On-Time Delivery
g.	Defects after Delivery
h.	Response Time

### Step 1

Data Structure of Dealer Satisfaction, End-User Satisfaction, Complaints, Mower Unit Sales, Tractor Unit Sales, On-Time Delivery, Defects after Delivery, Response Time:

```{r}

str(DealerSat)
str(EndUserSat)
str(Complaints)
str(MowerUnitSales)
str(TractorUnitSales)
str(OnTimeDelivery)
str(DefectsAfterDelivery)
str(ResponseTimesCSC)

```

Massage the Data for Plotting:

##**Dealer Satisfaction by Region:**

Prepare Data for the different Regions:

```{r}

yearsCols <- c("2010", "2011", "2012", "2013", "2014")
dataTags <- c("Level", "Year", "Counts")

```

###*North America:*

```{r}

naDealerSat <- DealerSat %>%
        sectionTranspose(1,5, 3,8) %>%
        tGraphData(yearsCols,dataTags)
ggplot(naDealerSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), position="dodge", stat="identity")
ggplot(naDealerSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), stat="identity")

```

###*South America:*

```{r}

saDealerSat <- DealerSat %>%
        sectionTranspose(6,10, 3,8) %>%
        tGraphData(yearsCols,dataTags)
ggplot(saDealerSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), position="dodge", stat="identity")
ggplot(saDealerSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), stat="identity")

```

###*Europe:*

```{r}

euDealerSat <- DealerSat %>%
        sectionTranspose(11,15, 3,8) %>%
        tGraphData(yearsCols,dataTags)
ggplot(euDealerSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), position="dodge", stat="identity")
ggplot(euDealerSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), stat="identity")

```

###*Pacific Rim:*

```{r}

prDealerSat <- DealerSat %>%
        sectionTranspose(16,20, 3,8) %>%
        tGraphData(yearsCols,dataTags)
ggplot(prDealerSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), position="dodge", stat="identity")
ggplot(prDealerSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), stat="identity")

```

###*China:*

```{r}

yearsInChinaCols <- c("2012", "2013", "2014")

chDealerSat <- DealerSat %>%
        sectionTranspose(21,23, 3,8) %>%
        tGraphData(yearsInChinaCols,dataTags)
ggplot(chDealerSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), position="dodge", stat="identity")
ggplot(chDealerSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), stat="identity")

```

##**Dealer Satisfaction by Region:**

###*North America:*

```{r}

naEndUserSat <- EndUserSat %>%
        sectionTranspose(1,5, 3,8) %>%
        tGraphData(yearsCols,dataTags)
ggplot(naEndUserSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), position="dodge", stat="identity")
ggplot(naEndUserSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), stat="identity")

```

###*South America:*

```{r}

saEndUserSat <- EndUserSat %>%
        sectionTranspose(6,10, 3,8) %>%
        tGraphData(yearsCols,dataTags)
ggplot(saEndUserSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), position="dodge", stat="identity")
ggplot(saEndUserSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), stat="identity")

```

###*Europe:*

```{r}

euEndUserSat <- EndUserSat %>%
        sectionTranspose(11,15, 3,8) %>%
        tGraphData(yearsCols,dataTags)
ggplot(euEndUserSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), position="dodge", stat="identity")
ggplot(euEndUserSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), stat="identity")

```

###*Pacific Rim:*

```{r}

prEndUserSat <- EndUserSat %>%
        sectionTranspose(16,20, 3,8) %>%
        tGraphData(yearsCols,dataTags)
ggplot(prEndUserSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), position="dodge", stat="identity")
ggplot(prEndUserSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), stat="identity")

```

###*China:*

```{r}

yearsInChinaCols <- c("2012", "2013", "2014")

chEndUserSat <- EndUserSat %>%
        sectionTranspose(21,23, 3,8) %>%
        tGraphData(yearsInChinaCols,dataTags)
ggplot(chEndUserSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), position="dodge", stat="identity")
ggplot(chEndUserSat, aes(x=Year, y=Counts)) + geom_bar(aes(fill=Level), stat="identity")

```

### Step 2

```{r}

plot(Complaints$World, ylim=range(c(0, 400)), type="l", xlab="Month", ylab="Number of Complaints")
par(new=TRUE)
plot(Complaints$'NA', ylim=range(c(0,400)), type="l", col="red", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)
plot(Complaints$SA, ylim=range(c(0,400)), type="l", col="green", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)
plot(Complaints$Eur, ylim=range(c(0,400)), type="l", col="blue", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)
plot(Complaints$Pac, ylim=range(c(0,400)), type="l", col="magenta", axes = FALSE, xlab = "", ylab = "")
par(new=TRUE)
plot(Complaints$China, ylim=range(c(0,400)), type="l", col="deeppink4", axes = FALSE, xlab = "", ylab = "")

```

## Part 2

### Step 1

```{r}

summary(UnitShippingCost$Mowers) #summary(ShippingCost_Existing$Mowers)
summary(UnitShippingCost$Tractors) #summary(ShippingCost_Existing$Tractors)
# Where is the ShippingCost_Proposed coming from?
# summary(ShippingCost_Proposed$Mowers)
# summary(ShippingCost_Proposed$Tractors)

```

## Part 3

### Step 1

```{r}

str(CustomerSurvey2014)
summary(CustomerSurvey2014)

CustomerSurvey2014[is.na(CustomerSurvey2014)] <- "NorthA"
str(CustomerSurvey2014)

barplot(table(CustomerSurvey2014$Region))

hist(CustomerSurvey2014$Quality, main="Quality - Number of Responses", xlab="Level of Quality")

```

### Step 2

## Part 4

TODO: Do this part as you best see fit in terms of a choice of a dashboard

#Chapter 4

## Part 1

For the Performance Lawn Equipment case study at the end of Chapter 4 you are tasked with developing the following:
a.	The mean satisfaction ratings and standard deviations by year and region in the data files Dealer Satisfaction and End-User Satisfaction
b.	A descriptive statistical summary for the 2014 customer survey data
c.	How the response times differ in each quarter of the data file Response Time
d.	How defects after delivery (data file Defects after Delivery) have changed over the years
e.	How sales of mowers and tractors compare with industry totals and how strongly monthly product sales are correlated with industry sales

### Step 1 (Part a)

```{r}

tDealerSat_NA <- DealerSat %>%
                 sectionTranspose(1,5, 3,8)
colnames(tDealerSat_NA) <- yearsCols
tDealerSat_NA # The transpose of the Dealer Satisfaction data for the North America region with column headings

m_NA2010 <- ((tDealerSat_NA[2,1]*1) + (tDealerSat_NA[3,1]*2) + (tDealerSat_NA[4,1]*3) + (tDealerSat_NA[5,1]*4) + (tDealerSat_NA[6,1]*5))/sum(tDealerSat_NA[,1])
m_NA2010

```

The easier brute force is:

```{r}

m=0
for (j in 1:25){
    # print(j)
    m[j] <- ((DealerSat[j,4]*1) + (DealerSat[j,5]*2) +
             (DealerSat[j,6]*3) + (DealerSat[j,7]*4)
             +(DealerSat[j,8]*5))/sum(DealerSat[j,3:8])
   # print(m[j])
}
print(m)

n <- matrix(m, 5, byrow=FALSE)
n

```

The same process is used for the standard deviations:

TODO: Revisit this!!
```{r}

m=0
n=0
# for (j in 1:25){
#     # print(j)
#     m[j] <- ((DealerSat[j,4]*1) + (DealerSat[j,5]*2) +
#                  (DealerSat[j,6]*3) + (DealerSat[j,7]*4)
#              +(DealerSat[j,8]*5))/sum(DealerSat[j,3:8])
#     n[j] <- sqrt(((DealerSat[j,3] * (0 - m[j])^2) + 
#                  (DealerSat[j,4] * (1 - m[j])^2) +
#                  (DealerSat[j,5] * (2 - m[j])^2) +
#                  (DealerSat[j,6] * (3 - m[j])^2) +
#                  (DealerSat[j,7] * (4 - m[j])^2) +
#                  (DealerSat[j,8] * (5 - m[j])^2))/
#                    (sum(DealerSat[j,3:8])-1))
#     # print(m[j])
#     # print(n[j])
# }
print(m)
print(n)

```

### Step 2 (Part b)

```{r}

custSurveyNA <- CustomerSurvey2014[1:100,-1]
custSurveySA <-CustomerSurvey2014[102:151,-1]

describe(custSurveySA)
stat.desc(custSurveySA)

```

### Step 3 (Part c)

```{r}

str(ResponseTimesCSC)

mResponseTimesCSC <- c(mean(ResponseTimesCSC$'Q1 2013'), mean(ResponseTimesCSC$'Q2 2013'), mean(ResponseTimesCSC$'Q3 2013'), mean(ResponseTimesCSC$'Q4 2013'), mean(ResponseTimesCSC$'Q1 2014'), mean(ResponseTimesCSC$'Q2 2014'), mean(ResponseTimesCSC$'Q3 2014'), mean(ResponseTimesCSC$'Q4 2014'))
mResponseTimesCSC

plot(mResponseTimesCSC, type = "l", lwd=2, col="green", ylab = "Mean", xlab = "Quarter", main="Mean Response Time", ylim = c(0,5), xaxt="n")
#TODO: Revisit this!!!!
#axis(side = 1, at = c(1:8), labels = alabels, pch=0.5)

```

### Step 4 (Part d)

```{r}

str(DefectsAfterDelivery)

```

TODO: Complete this part of the exercise

### Step 5 (Part e)

```{r}

str(MowerUnitSales)
str(IndustryMowerTotalSales)

totalMowerSales <- MowerUnitSales[,]
str(totalMowerSales)

totalMowerSales[,8:12]<- IndustryMowerTotalSales[,-1]
str(totalMowerSales)

#TODO: Revisit this
#colnames(totalMowerSales) <- c("Month", "Year", "NorthA", "SA", "Eur", "Pac", "China", "World", "IndustryNorthA", "IndustrySA", "IndustryEur", "IndustryPac", "IndustryWorld")
#head(totalMowerSales)

stat.desc(totalMowerSales)
rcorr(as.matrix(totalMowerSales[3:12]))

```

# Chapter 5

## Part 1

### Step 1

Answer: Bernoulli Distribution

### Step 2

```{r}

countFail <- length(which(MowerTest == "Fail"))
countFail

```

So there are 54 “Fail” in the MowerTest data set, or the fraction of “Fail”, i.e. the probability of “Fail” is 54/3000 = 0.018. 

### Step 3

```{r}

y <- dbinom(0:20, 100, .018)
y
plot(y)

```

### Step 4

```{r}


View(BladeWeight)
str(BladeWeight)

(sum(BladeWeight$Weight)/350)
sd(BladeWeight$Weight)

```

### Step 5

```{r}

y = pnorm(5.20, mean=4.99, sd=0.11)
y
1 - y

```

### Step 6

```{r}


pnorm(4.80, mean=4.99, sd=0.11)
```

### Step 7

```{r}

countblade <- length(which(BladeWeight$Weight > 5.20))
countblade
countblade2 <- length(which(BladeWeight$Weight <= 4.80))
countblade2

```

### Step 8

```{r}


plot(BladeWeight$Sample, BladeWeight$Weight)
```

### Step 9

Looking at the scatter plot, only close to the 200th blade was there any trouble.  It isn’t too much trouble to find that this is blade #171.

### Step 10

```{r}

hist(BladeWeight$Weight)

```

# Chapter 6

## Part 1

### Step 1

```{r}

countByRegion <- table(CustomerSurvey2014$Region, CustomerSurvey2014$Quality)
countByRegion

sum(countByRegion[3,4], countByRegion[3,5])

```

### Step 2

````{r}

Q1.13mean <- mean(ResponseTimesCSC$'Q1 2013')
Q1.13std <- sd(ResponseTimesCSC$'Q1 2013')

Q1.13mean
Q1.13std

z.test(ResponseTimesCSC$'Q1 2013', sigma.x = Q1.13std)

Q2.13mean <- mean(ResponseTimesCSC$'Q2 2013')
Q2.13std <- sd(ResponseTimesCSC$'Q2 2013')
z.test(ResponseTimesCSC$'Q2 2013', sigma.x = Q2.13std)

````

### Step 3

```{r}

current.sd <- sd(TransmissionCosts$Current)
z.test(TransmissionCosts$Current, sigma.x = current.sd)

```

### Step 4

\begin{equation}
Standard\hspace{1 mm}deviation = \sqrt{\frac{mean * (1 - mean)}{n}}
\end{equation}

```{r}

#TODO: Revisit this!!!!
A <- data.frame(lapply(MowerTest, function(x) as.numeric(x)))
str(A)
A[,5] <- 2
A[,10] <- 2
A[,27] <- 2
A[,30] <- 2
str(A)

B <- data.matrix(A[,-1])
str(B)
B <- B - 1
str(B)

B <- B - 1
length(which(B==0))
1-mean(B)
t.test(B, mu=0.982)
#End TODO

hist(BladeWeight$Weight)

# The standard error of the mean for our blade weight data can be found using
sem <- sd(BladeWeight$Weight)/sqrt(length(BladeWeight$Weight))
sem

#TODO: Revisit this!
A <- lm(BladeWeight$Weight~ ., BladeWeight)
str(A)
plot(A)

```

###*Other Stuff to Revisit:*

```{r}

seq(1,16)
seq(32)
c(4,4,2)

?apply

M <- matrix(seq(1,16), 4, 4)
M

# apply min/max to rows
apply(M, 1, min)
apply(M, 1, max)

# apply min/max to columns
apply(M, 2, min)
apply(M, 2, max)

# 3 dimensional array
M <- array( seq(32), dim = c(4,4,2) )
M

# apply sum across each M[*, , ] - i.e sum across 2nd and 3rd dimension
apply(M, 1, sum)

# apply sum across each M[*, , ] - i.e sum across 3rd dimension
apply(M, c(1,2), sum)

# result is two-dimension

```

```{r}

str(DealerSat)

```

```{r}

#View, Structure
#View(CustomerSurvey2014)
#str(CustomerSurvey2014)

#View(BladeWeight)
#str(BladeWeight)

## #Next identify the N/A rows
## is.na(BladeWeight$Sample)
## is.na(BladeWeight$Weight)

## #Next reverse tge vector of truefalse using a boolean-not operation
## BladeWeight[!is.na(BladeWeight$Sample),]

## #Delete the rows
## BladeWeight = BladeWeight[!is.na(BladeWeight$Sample),]

## #Verify it worked
## summary(BladeWeight$Sample)

## #Finally let's subset the data by region. ##
## View(Dealer_Sat)
## dealerSat_NA = Dealer_Sat[1:5,]
## dealerSat_NA
## View(dealerSat_NA)
## head(dealerSat_NA)

## tdealerSat_NA = t(dealerSat_NA[,3:8])
## tdealerSat_NA
## View(tdealerSat_NA)

## colnames(tdealerSat_NA) <- c("2010", "2011", "2012", "2013", "2014")
## head(tdealerSat_NA)
## colnames(tdealerSat_NA)

```

This is how you create an appendix with R Markdown

#### A Sample Plot

```{r sample_plot, echo=FALSE}

# Define 2 vectors
cars <- c(1, 3, 6, 4, 9)
trucks <- c(2, 5, 4, 5, 12)

# Graph cars using a y axis that ranges from 0 to 12
plot(cars, type="o", col="blue", ylim=c(0,12))

# Graph trucks with red dashed line and square points
lines(trucks, type="o", pch=22, lty=2, col="red")

# Create a title with a red, bold/italic font
title(main="Autos", col.main="red", font.main=4)

```

See Appendix [Code for A Sample Plot]

### Another Sample Plot

```{r samplePlot, echo=FALSE}
```

See Appendix [Code for Another Sample Plot]

## DELETE THIS CHUNK LATER
```{r}

#head(DealerSat)
#stat.desc(DealerSat)

#library(help = "stats")
#library(help = "pastecs")

```

# Appendix

### Code for A Sample Plot
```{r sample_plot2, ref.label='sample_plot', eval=FALSE}
```

### Code for Another Sample Plot
```{r samplePlot}
```

# References

