---
title: "ANLY 502 Group Project Data"
author: "Akpany Benjamin Ebby"
date: "April 27th, 2018"
output:
  pdf_document:
    highlight: zenburn
comment: Rmd Document with Markdown + Embedded R Code
---

#### Document as of `r Sys.Date()`

```{r setup, include=FALSE, purl=FALSE, eval=TRUE}

source('R/ANLY502_GroupProjectData_Helper.R')

```

```{r echo=FALSE}

library(knitr)
read_chunk('R/ANLY502_GroupProjectData_Chunks.R')

```

*Install the Required Libraries if not installed*
```{r installLibraries}
```

*Load the Required Libraries*
```{r loadLibraries}
```

Some helper functions do exists to support the code snippets below such as: ```loadSheetFromFile```

#General Description of Data

The AWS Honeypot Database is an open-source database including information on cyber attacks/attempts.
Data has 451,581 data points collected from 9:53pm on 3 March 2013 to 5:55am on 8 September 2013

###*Set Data File Name:*

```{r}

attackDataFile <- "AWS_Honeypot_marx-geo.csv"

```

###*AWS Honeypot Attack Data*

The Data is in the CSV format with a size of ```47MB```, and is a ```6MB``` zipped download.

*Load Data*

```{r}

# Honeypot Attack
HoneypotAttack <- loadSheetFromFile(attackDataFile, skip = 0)
```

*Summary of Data*

```{r}
summary(HoneypotAttack)
```


*Structure of Data*

```{r}
str(HoneypotAttack) #Good way to quickly show the structure of something
```

*Description of Data*

```{r}
stat.desc(HoneypotAttack)
```

#List of explanatory variables

The explanatory variables are:	**src,	proto, type, spt, dpt, srcstr, cc, country, locale, localeabbr**

###src:
designates the origin of the attack

#Data Source

[Kaggle: AWS Honeypot Attack Data](https://www.kaggle.com/casimian2000/aws-honeypot-attack-data)
```
https://www.kaggle.com/casimian2000/aws-honeypot-attack-data
```


